A pipeline to analyse time-course gene expression data

### 2020-08-31 scripts/manuscript.Rmd
Packages are now (almost) on bioconductor

```{r eval=FALSE}
BiocManager::install(
    c("NMF", "ggfortify", "topGO", "biomaRt",
      "KEGGprofile", "BiocWorkflowTools"))
```

@@

This workflow is illustrated using data from a micro-array time-course
experiment, exposing mice to three different strains of influenza, and
collecting lung tissue during 14 time-points after infection (0, 3, 6, 9, 12,
18, 24, 30, 36, 48, 60 hours, then 3, 5, and 7 days later)
[@shoemaker:ultrasensitive]. The three strains of influenza used in the
study are (1) a low pathogenicity seasonal H1N1 influenza virus
(A/Kawasaki/UTK4/2009 [H1N1]), a mildly pathogenic virus from the 2009
pandemic season (A/California/04/2009 [H1N1]), and a highly pathogenic H5N1
avian influenza virus (A/Vietnam/1203/2004 [H5N1]. Mice were injected with
$10^5$ PFU of each virus. An adidtional 42 mice were injected with a lower dose
of the Vietnam avian influenza virus ($10^3$ PFU).

>>>>

```{r eval=FALSE}
BiocManager::install(
    c("NMF", "ggfortify", "topGO", "biomaRt",
      "KEGGprofile", "BiocWorkflowTools", "timecoursedata", ))
```

@@

This workflow is illustrated using data from a micro-array time-course
experiment, exposing mice to three different strains of influenza, and
collecting lung tissue during 14 time-points after infection (0, 3, 6, 9, 12,
18, 24, 30, 36, 48, 60 hours, then 3, 5, and 7 days later)
[@shoemaker:ultrasensitive]. The three strains of influenza used in the
study are (1) a low pathogenicity seasonal H1N1 influenza virus
(A/Kawasaki/UTK4/2009 [H1N1]), a mildly pathogenic virus from the 2009
pandemic season (A/California/04/2009 [H1N1]), and a highly pathogenic H5N1
avian influenza virus (A/Vietnam/1203/2004 [H5N1]. Mice were injected with
$10^5$ PFU of each virus. An additional 42 mice were injected with a lower dose
of the Vietnam avian influenza virus ($10^3$ PFU).
